---
title: "project_merged"
output: html_document
---
microbes graph code

```{r}
library(readr)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(janitor)
```

```{r}
clean_data_mold <- read_csv("Microbes_new/clean_data_mold.csv")
View(clean_data_mold)
```

```{r}
names(clean_data_mold)
```

```{r}
clean_data_mold %>% 
  select(Section,`Total Colony counts`) %>%
  ggplot(aes(x=Section,y=`Total Colony counts`,fill = Section))+
  geom_col() #section and total colony counts
```

```{r}
clean_data_mold %>% 
  select(Section,"# Bacteria looking colonies") %>% 
  ggplot(aes(x=Section,y=`# Bacteria looking colonies`,fill = Section))+
  geom_col() #section and bacteria
```

```{r}
clean_data_mold %>% 
  select(Section,"# Mold looking colonies \n(Hyphae)") %>% 
  ggplot(aes(x=Section,y=`# Mold looking colonies \n(Hyphae)`,fill = Section))+
  geom_col() #section and mold
```

```{r}
clean_data_mold2 <- clean_data_mold %>% 
pivot_longer(cols="Inside or Outside",
             values_to = "Location") %>% 
  clean_names() %>% 
  mutate(location=str_to_title(location))
```

```{r}
names(clean_data_mold2)
```

```{r}
clean_data_mold2 %>% 
  select(location,number_bacteria_looking_colonies,number_mold_looking_colonies_hyphae) %>%
  ggplot(aes(x=number_bacteria_looking_colonies,y=number_mold_looking_colonies_hyphae,color=location))+
  geom_jitter(size=2.8,alpha=.8) #bacteria and mold vs inside outside
```

```{r}
clean_data_mold3 <- clean_data_mold2 %>% 
  pivot_longer(cols = "media_additive",
               names_to = "media_additive",
               values_to = "media_add") %>% 
  mutate(media_add=str_to_title(media_add))
```

```{r}
clean_data_mold3 %>% 
  select(media_add)
```

```{r}
clean_data_mold3 %>%
  select(media_add,number_bacteria_looking_colonies) %>%
  ggplot(aes(x=media_add,y=number_bacteria_looking_colonies,color=media_add))+
  geom_boxplot() #media add and bacteria
```

```{r}
clean_data_mold3 %>%
  select(media_add,number_mold_looking_colonies_hyphae) %>%
  ggplot(aes(x=media_add,y=number_mold_looking_colonies_hyphae,color=media_add))+
  geom_boxplot() #media add and mold
```

```{r}
names(clean_data_mold3)
```

```{r}
clean_data_mold3 %>% 
  select(section,media_add) %>% 
  filter(media_add=="Amp") %>% 
  count(media_add) %>% 
  ggplot(aes(x=section,y=n,fill=section))+
  geom_col() #why no work?
```
## microbes graph code 2:

```{r}
clean_data_mold <- read_csv("C:/Users/lalva/OneDrive/Desktop/BIS015L_W2026_Group6-main/Microbes_new/clean_data_mold.csv")
View(clean_data_mold)
```

```{r}
names(clean_data_mold)
```

```{r}
clean_data_mold %>% 
  select(Section,`Total Colony counts`) %>%
  ggplot(aes(x=Section,y=`Total Colony counts`,fill = Section))+
  geom_col() #section and total colony counts
```

```{r}
clean_data_mold %>% 
  select(Section,"# Bacteria looking colonies") %>% 
  ggplot(aes(x=Section,y=`# Bacteria looking colonies`,fill = Section))+
  geom_col() #section and bacteria
```

```{r}
clean_data_mold %>% 
  select(Section,"# Mold looking colonies \n(Hyphae)") %>% 
  ggplot(aes(x=Section,y=`# Mold looking colonies \n(Hyphae)`,fill = Section))+
  geom_col() #section and mold
```






clean_data_mold2 <- clean_data_mold %>% 
  pivot_longer(cols="Inside or Outside",
               values_to = "Location") %>% 
  clean_names() %>% 
  mutate(location=str_to_title(location))

names(clean_data_mold2)

clean_data_mold2 %>% 
  select(location,number_bacteria_looking_colonies,number_mold_looking_colonies_hyphae) %>%
  ggplot(aes(x=number_bacteria_looking_colonies,y=number_mold_looking_colonies_hyphae,color=location))+
  geom_jitter(size=2.8,alpha=.8) #bacteria and mold vs inside outside, dot plot is not great try something else




clean_data_mold3 <- clean_data_mold2 %>% 
  pivot_longer(cols = "media_additive",
               names_to = "media_additive",
               values_to = "media_add") %>% 
  mutate(media_add=str_to_title(media_add))

clean_data_mold3 %>% 
  select(media_add)

clean_data_mold3 %>%
  select(media_add,number_bacteria_looking_colonies) %>%
  ggplot(aes(x=media_add,y=number_bacteria_looking_colonies,color=media_add))+
  geom_boxplot() #media add and bacteria

clean_data_mold3 %>%
  select(media_add,number_mold_looking_colonies_hyphae) %>%
  ggplot(aes(x=media_add,y=number_mold_looking_colonies_hyphae,color=media_add))+
  geom_boxplot() #media add and mold

names(clean_data_mold3)

clean_data_mold3 %>% 
  select(section,media_add) %>% 
  filter(media_add=="Amp") %>% 
  count(media_add) %>% 
  ggplot(aes(x=section,y=n,fill=section))+
  geom_col() #why no work?


  clean_data_mold3 %>% 
    select(exposure_duration_min,total_colony_counts, media_add) %>% 
    ggplot(aes(x=exposure_duration_min,y=total_colony_counts, color = media_add,group=media_add))+
    stat_summary(fun=mean, geom="line",linewidth=1)+
    stat_summary(fun=mean, geom="point",size=3)



#Microbes Graphs for 2023
library(tidyverse)
library(googlesheets4)
library(janitor)

library(readr)
Microbes_data_2023 <- read_csv("C:/Users/lalva/OneDrive/Desktop/BIS015L_W2026_Group6-main/Microbes_new/Microbes data - 2023.csv")
View(Microbes_data_2023)

#This is for pivoting locations
Microbes_data_2023 <-  Microbes_data_2023 %>% 
  pivot_longer(cols="Inside or Outside",
               values_to = "Location") %>% 
  clean_names() %>% 
  mutate(location=str_to_title(location))

#This is for pivioting additives
Microbes_data_2023 <- Microbes_data_2023 %>% 
  pivot_longer(cols = "media_additive_none_cyc_or_amp",
               names_to = "media_additive",
               values_to = "media_add") %>% 
  mutate(media_add=str_to_title(media_add))


#Bar Graph Visualization

Microbes_data_2023 %>% 
  select(section,total_number_colonies) %>%
  ggplot(aes(x=section,y=total_number_colonies,fill = section))+
  geom_col()+
  labs(title = "Section per Total Colony Counts")

Microbes_data_2023 %>% 
  select(section,number_non_mold_like_colonies_e_g_no_hyphae) %>% 
  ggplot(aes(x=section,y=number_non_mold_like_colonies_e_g_no_hyphae,fill = section))+
  geom_col()+
  labs(title = "Section per Bacteria Looking Colonies")

Microbes_data_2023 %>% 
  select(section,number_mold_like_colonies_have_hyphae) %>% 
  ggplot(aes(x=section,y=number_mold_like_colonies_have_hyphae,fill = section))+
  geom_col()+
  labs(title = "Section per Mold Looking Colonies")


#Boxplot Graph Visualization

#To enable Faceting Otherwise Unneccicary
Microbes_data_2023_2 <- Microbes_data_2023 %>% 
  pivot_longer(cols = c("number_non_mold_like_colonies_e_g_no_hyphae","number_mold_like_colonies_have_hyphae"),
               names_to = "colony_type",
               values_to = "colony_count")
Microbes_data_2023_2 %>% 
  ggplot(aes(x=location, y=colony_count, fill = colony_type))+
  geom_boxplot(position = position_dodge(width=.8))+
  facet_wrap(~location, scales="free")

Microbes_data_2023 %>% 
  select(media_add,number_non_mold_like_colonies_e_g_no_hyphae) %>%
  ggplot(aes(x=media_add,y=number_non_mold_like_colonies_e_g_no_hyphae,color=media_add))+
  geom_boxplot()+
  labs(title = "Media Additive per Bacteria Looking Colonies")

Microbes_data_2023 %>%
  select(media_add,number_mold_like_colonies_have_hyphae) %>% 
  ggplot(aes(x=media_add,y=number_mold_like_colonies_have_hyphae,color=media_add))+
  geom_boxplot()+
  labs(title = "Media Additive per Mold Looking Colonies")


#Line Graph Visualization

Microbes_data_2023 %>%
  group_by(media_add, exposure_duration_min) %>%
  summarize(mean_colony_counts = mean(total_number_colonies, na.rm = TRUE)) %>%
  ggplot(aes(x=exposure_duration_min,
             y=mean_colony_counts, 
             group=media_add,
             color=media_add))+
  geom_line()
  
  
  #Microbes Graphs for 2026
library(tidyverse)
library(googlesheets4)
library(janitor)

library(readr)
clean_data_mold <- read_csv("C:/Users/lalva/OneDrive/Desktop/BIS015L_W2026_Group6-main/Microbes_new/clean_data_mold.csv")
View(clean_data_mold)

#Cleaning
clean_data_mold <- clean_data_mold %>%
  clean_names()

#This is for pivoting locations
clean_data_mold <-  clean_data_mold %>% 
  pivot_longer(cols="inside_or_outside",
               values_to = "location") %>% 
  mutate(location=str_to_title(location))

#This is for pivioting additives
clean_data_mold <- clean_data_mold %>% 
  pivot_longer(cols = "media_additive",
               names_to = "media_additive",
               values_to = "media_add") %>% 
  mutate(media_add=str_to_title(media_add))

#Bar Graph Visualization

clean_data_mold %>% 
  select(section,total_colony_counts) %>%
  ggplot(aes(x=section,y=total_colony_counts,fill = section))+
  geom_col()+
  labs(title = "Section per Total Colony Counts")

clean_data_mold %>% 
  select(section,number_bacteria_looking_colonies) %>% 
  ggplot(aes(x=section,y=number_bacteria_looking_colonies,fill = section))+
  geom_col()+
  labs(title = "Section per Bacteria Looking Colonies")

clean_data_mold %>% 
  select(section,number_mold_looking_colonies_hyphae) %>% 
  ggplot(aes(x=section,y=number_mold_looking_colonies_hyphae,fill = section))+
  geom_col()+
  labs(title = "Section per Mold Looking Colonies")


#Boxplot Visualization

#To enable Faceting Otherwise Unneccicary
clean_data_mold2 <- clean_data_mold %>% 
  pivot_longer(cols = c("number_bacteria_looking_colonies","number_mold_looking_colonies_hyphae"),
               names_to = "colony_type",
               values_to = "colony_count")
clean_data_mold2 %>% 
  ggplot(aes(x=location, y=colony_count, fill = colony_type))+
  geom_boxplot(position = position_dodge(width=.8))+
  facet_wrap(~location, scales="free")

clean_data_mold %>%
  select(media_add,number_bacteria_looking_colonies) %>%
  ggplot(aes(x=media_add,y=number_bacteria_looking_colonies,color=media_add))+
  geom_boxplot()+
  labs(title = "Media Additive per Bacteria Looking Colonies")

clean_data_mold %>%
  select(media_add,number_mold_looking_colonies_hyphae) %>%
  ggplot(aes(x=media_add,y=number_mold_looking_colonies_hyphae,color=media_add))+
  geom_boxplot()+
  labs(title = "Media Additive per Mold Looking Colonies")

#Line Graph Visualization

clean_data_mold %>%
  group_by(media_add, exposure_duration_min) %>%
  summarize(mean_colony_counts = mean(total_colony_counts, na.rm = TRUE)) %>%
  ggplot(aes(x=exposure_duration_min,
             y=mean_colony_counts, 
             group=media_add,
             color=media_add))+
  geom_line()
  
  
#  app code
library(shiny)
```{r, eval=F, echo=T}
ui <- dashboardPage(
  
  dashboardHeader(title="Microbe Data"),
  
  dashboardSidebar(
  
    selectInput("year",
              "Dataset Year:",
              choices=sortc("2023", "2024","2026")),
              selected="2023"),
    
    selectInput("plot",
              "Select Plot Type",
              choices = c("bar", "boxplot", "line"),
              selected="bar"),
  
    selectInput("x",
              "Select X Axis",
              choices = c("bar", "boxplot", "line"),
              selected="bar"),
  
      selectInput("y",
              "Select Y Axis",
              choices = c("bar", "boxplot", "line"),
              selected="bar")
    
  ),
    
    dashboardBody(
      
    plotOutput("plot", width="500px", height="400px")
    
  )
  
)

server <- function(input, output, session) {
  
  output$plot <- renderPlot({
    
    clean_data_mold %>% 
      filter(input$x==.data[["order"]]) %>% 
      ggplot(aes(.data[[input$y]]))+
      geom_density(fill="steelblue",
                   color="black",
                   alpha=0.6)+
      theme_light()
    
    
    if input$plot == "bar" {
      clean_data_mold %>% 
        ggplot(aes(x = section, y = total_colony_counts, fill = section)) +
        geom_col() +
        labs(title = "Total Colony Counts per Section") 
      }
    
    else if input$plot == "boxplot" {
      clean_data_mold %>%   
        ggplot(aes(x = media_add, y = number_bacteria_looking_colonies, color = media_add)) +
        geom_boxplot() +
        labs(title = "Bacteria Colonies by Media Additive")
      }
    
    else if input$plot == "line" {
      clean_data_mold %>% 
       ggplot(aes(x = exposure_time?, y = number_bacteria_looking_colonies, color = media_add)) +
        geom_line() +
        labs(title = "Growth Over Time")
      }
    
  })
  
}

shinyApp(ui, server)
```



